\newglossaryentry{MachineLearning}
{
name={Machine Learning},
description={Field of computer science with the aim of developing algorithms that automatically improve performance based on supplied examples \cite{glossarymachinelearning}} 
}
\newglossaryentry{SciFinder}
{
name={SciFinder\textsuperscript{\textregistered}},
description={Bibliographic and citation search engine provided by the American Chemical Society designed for chemical research} 
}
\newglossaryentry{WebOfScience}
{
name={Web Of Science	\textsuperscript{TM}},
description={Bibliographic and citation search engine provided by Thomson Reuters} 
}
\newglossaryentry{Scraping}
{
name={Scraping},
description={Programming technique to automatically extract data from online resources} 
}
\newglossaryentry{Crawling}
{
name={Crawling},
description={Programming technique to automatically navigate through the online landscape identifying candidate websites for scraping (See Scraping)} 
}
\newglossaryentry{Metadata}
{
name={Meta-data},
description={Meta-data refers to data about data. In the context of this project, it refers to data describing a chemistry article, i.e. title, abstract, DOI (See DOI), authors, affiliations, journal, publisher and date of publication}
}
\newglossaryentry{python}
{
name={Python},
description={Interpreted, dynamically typed programming language. Unless explicitly mentioned, Python was the language used for all development and analysis in this project} 
}
\newglossaryentry{MongoDB}
{
name={MongoDB},
description={Schema-less `NoSQL' database used for document storage retrieval} 
}
\newglossaryentry{HTML}
{
name={HTML},
description={Hypertext Markup Language. Tag-based language to encode web-pages in a hierarchical structure. Webpages are written as HTML files, which are interpreted by internet browsers to display the page's content to users} 
}
\newglossaryentry{XML}
{
name={XML},
description={eXtensible Markup Language. Tag-based markup language, closely related to HTML. Method of encoding any type of data in a manner that is machine readable and intelligible by humans} 
}
\newglossaryentry{XPath}
{
name={XPath},
description={Query method for extracting data from XML documents. As HTML is closely related to XML, XPath strings can be used to access data in HTML documents} 
}
\newglossaryentry{REGEX}
{
name={REGEX},
description={REGular EXpression. A REGEX is a string that is used to inform a programming language of patterns to identify in a body of text} 
}
\newglossaryentry{DOI}
{
name={DOI},
description={Digital Object Identifier. Unique identifier string used to index the vast majority of academic literature articles published since 2000 \cite{glossarydoi}} 
}
\newglossaryentry{Crossref}
{
name={Crossref},
description={Crossref is an organisation promoting inter-publisher cooperation. With a mission statement to `support ... persistent, sustainable infrastructure for scholarly communication'\cite{crossref-formation}. Crossref provides  tools for researchers to access a wide range of publishers' materials} 
}
\newglossaryentry{PILA}
{
name={PILA},
description={Publishers International Linking Association, Inc. . Independent not-for-profit body comprised of scientific prublishing entities. PILA operates Crossref \cite{crossref-formation}} 
}
\newglossaryentry{IDF}
{ 
name={IDF},
description={International Doi Foundation. Independent not-for-profit body which governs the use and management of the DOI system. Provide definitive service for resolving a DOI to its document \cite{doi_handbook2}} 
}
\newglossaryentry{UTF-8}
{
name={UTF-8},
description={Universal Coded Character Set + Transformation Format – 8-bit \cite{utf8}. An encoding specification for the Unicode character set, where each character is encoded by 8 bits. UTF-8 is the dominant encoding used online \cite{utf8stats}} 
}
\newglossaryentry{Unicode}
{
name={Unicode},
description={Standard for encoding characters used in worldwide communication. The Unicode character set of 120,000 characters includes mathematical symbols, punctuation, and character languages (Mandarin, Japanese etc.)} 
}
\newglossaryentry{API}
{
name={API},
description={Application Programmer Interface. Set of well defined input and output operations to a program or service to enable programmers to easily use the service} 
}
\newglossaryentry{ACS}
{
name={ACS},
description={American Chemical Society. A Scientific society specialising in the chemistry domain with a large scientific academic publishing arm. The ACS also own the Chemical Abstracts Service and SciFinder\textsuperscript{\textregistered}} 
}
\newglossaryentry{TaylorFrancis}
{
name={Taylor \& Francis},
description={Part of the Informa group. An academic publisher covering a range of scientific disciplines} 
}
\newglossaryentry{IPADDRESS}
{
name={IP Address},
description={Internet Protocol Address. An IP address is the identifier for any computer or device using a network that runs on Internet Protocol} 
}
\newglossaryentry{d1}
{
name={$\Delta1$},
description={Database of article meta-data created from DOIs found on UK Chemistry department websites} 
}
\newglossaryentry{d2}
{
name={$\Delta2$},
description={Database of complete article meta-data including abstracts found on UK Chemistry department websites} 
}
\newglossaryentry{d3}
{
name={$\Delta3$},
description={Database of article meta-data created from DOIs found in global scraping procedure} 
} 
\newglossaryentry{d4}
{
name={$\Delta4$},
description={Database of complete article meta-data including abstracts found in global scraping procedure} 
}
\newglossaryentry{d5}
{
name={$\Delta5$},
description={Database created by combining databases $\Delta2$ and $\Delta4$} 
}
\newglossaryentry{d6}
{
name={$\Delta6$},
description={Database comprised of records in database $\Delta5$ deemed suitable for machine learning, i.e.  sufficiently long titles and abstracts and predominantly ascii characters} 
}
\newglossaryentry{d7}
{
name={$\Delta7$},
description={Database comprised of records in Database $\Delta6$ which had originated from DOIs found on the Cambridge University Chemistry Department} 
}
\newglossaryentry{RSC}
{
name={RSC},
description={Royal Society of Chemistry. British learn\`ed society for chemical sciences with an academic publishing arm} 
}
\newglossaryentry{Zipfslaw}
{
name={Zipf's Law},
description={States that the relationship of the log of the rank of a word to the log of the frequency of that word in a large corpus of text approximates a directly proportional relationship \cite{zipf}} 
}
\newglossaryentry{Corpus}
{
name={Corpus},
description={In the field of language processing, a corpus is a large body of natural language text. In the context of the project, a corpus is the combined titles and abstracts of all the records in a database} 
}
\newglossaryentry{NLP}
{
name={NLP},
description={Natural Language Processing. NLP is the field of linguistics and computer science with the aim of processing human written (natural) language with a computer} 
}
\newglossaryentry{BagOfWords}
{
name={Bag Of Words},
description={Simple Document Representation model which attempts to represent a document as a vector based on presence/absence of words} 
}
\newglossaryentry{BagOfCitations}
{
name={Bag Of Citations},
description={Simple Document Representation model which attempts to represent a document based on presence/absence of citations} 
}
\newglossaryentry{Word2vec}
{
name={Word2Vec},
description={Sophisticated distributed word vector model utilising a Neural Net to learn vector representations of  component words in a corpus by training sentence by sentence \cite{word2vec1}\cite{word2vec2}  } 
}
\newglossaryentry{NeuralNet}
{
name={Neural Net},
description={Data structure capable of developing decision pathways using supplied examples} 
}
\newglossaryentry{CBOW}
{
name={CBOW},
description={Continuous Bag Of Words. Learning architecture used by Word2Vec algorithm. Word Vector predictions are made from sum or mean of surrounding context words} 
}
\newglossaryentry{Skipgram}
{
name={Skipgram},
description={Learning architecture used by the Word2Vec algorithm. Word Vector predictions are made from random comparison between a word and nearby context words} 
}
\newglossaryentry{Doc2Vec}
{
name={Doc2Vec},
description={Gensim implementation of Paragraph Vectors algorithm (See Paragraph Vectors)} 
}
\newglossaryentry{Paragraphvectors}
{
name={Paragraph Vectors},
description={NLP algorithm based on Word2Vec for generating representation vectors for documents} 
}
\newglossaryentry{Stopwords}
{
name={Stop Words},
description={Words removed from a corpus before being processed. Stopwords are very common and/or do not encode significant information content} 
}
\newglossaryentry{Stemmer}
{
name={Stemmer},
description={An algorithm used to relate derived words (e.g. plurals, conjugated verbs) to their roots} 
}
\newglossaryentry{SNOWBALL}
{
name={Snowball},
description={Recent stemming algorithm \cite{snowball} (Also known as Porter2). Snowball is also the name of the programming language developed for stemming.} 
}
\newglossaryentry{Lancaster}
{
name={Lancaster},
description={Stemming algorithm \cite{lancaster}} 
}
\newglossaryentry{Porter}
{
name={Porter},
description={Early, widely used stemming algorithm \cite{porter}} 
}
\newglossaryentry{WordNet}
{
name={WordNet},
description={Lemmatizing stemming algorithm, based on consulting database of groups of semantically connected word concepts \cite{wordnet1} \cite{wordnet2} \cite{wordnet3}} 
}
\newglossaryentry{TF-IDF}
{
name={TF-IDF},
description={Term-Frequency Inverse-Document-Frequency. Method for assigning weights to words in a document for how much information the word carries} 
}
\newglossaryentry{Gensim}
{
name={Gensim},
description={Gensim is an open-source library for Python programs for use in NLP applications} 
}
\newglossaryentry{Hyperparameters}
{
name={Hyperparameters},
description={Adjustable Parameters used by a Machine Learning algorithm. Different to internal parameters automatically learnt by the algorithm} 
}
\newglossaryentry{TrainingEpoch}
{
name={Training  Epoch},
description={A complete iteration over the training data available to a learning algorithm} 
}
\newglossaryentry{CosineSim}
{
name={Cosine Similarity},
description={A similarity metric for vectors derived from the angle between them. $S_{cosine}=cos\left(\theta\right)$ for angle $\theta$ between two vectors} 
}
\newglossaryentry{euclideansim}
{
name={Euclidean Similarity},
description={A similarity metric for vectors derived from their distance in Euclidean space. $S_{euclid} = \sqrt{\sum_{i=1}^{D}(\nu_i^{\alpha}-\nu_i^{\beta})^{2}}$ for vectors $\alpha$ and $\beta$}
}
\newglossaryentry{PCA}
{
name={PCA},
description={Principle Component Analysis. Well established technique for reducing dimensionality by a series of orthogonal transformations \cite{PCA}} 
}
\newglossaryentry{TSNE}
{
name={TSNE},
description={T-distributed Stochastic Network Embedding. State of the art technique for reducing dimensionality by preserving spatial clusters of vectors at high dimensions \cite{TSNE}} 
}
\newglossaryentry{Hadamarddiv}
{
name={Hadamard Division},
description={Element-wise division matrix operation defined as $\left( \mathbf{A} \oslash \mathbf{B} \right)_{i , j} = \mathbf{A}_i / \mathbf{B}_j  $ for matrices $\mathbf{A}$ and $\mathbf{B}$} 
}
\newglossaryentry{Hadamardsqrt}
{
name={Hadamard Square Root},
description={Element-wise square root matrix operation defined as $\left( A^{\circ\frac{1}{2}} \right)_{i , j} = A_{i , j}^{\frac{1}{2}} $ for matrix A} 
}
\newglossaryentry{Gephi}
{
name={Gephi},
description={An open-source network visualisation, rendering and analysis application} 
}
\newglossaryentry{Communities}
{
name={Communities},
description={Subset of documents in a corpus identified via the Blondel-Guillaume-Lambiotte-Lefebvre modularity algorithm \cite{modularity1}\cite{modularity2}} 
}
\newglossaryentry{UPGMA}
{
name={UPGMA},
description={Unweighted Pair Group Method with Arithmetic Mean. Pairwise Clustering algorithm that partitions a set into hierarchical sub-set clusters using mean distances between pairs of elements \cite{heatmapcluster}} 
}
\newglossaryentry{Dendrogram}
{
name={Dendrogram},
description={Tree diagram used to illustrate relationships between clusters produced in hierarchical clustering procedures \cite{dendrogram}} 
}
\newglossaryentry{Clustermap}
{
name={Cluster Map},
description={A heat-map of two-dimensional data with axes arranged by a hierarchical clustering algorithm, often overlaid with dendrograms along each axes to illustrate clustering and spatial relationships \cite{dendrogram} \cite{seaborn} \cite{scipy}} 
}